Figures and Analysis for 2023 Manuscript

### 2023-11-14 data-raw/Manuscript2023_Workflow.Rmd
Added alternate figures and data variability calculations

```{r Final_Options}
my_pk <- minimal_pk +
  facet_data(vars(Chemical, Species)) +
  settings_preprocess(keep_data_original = TRUE,
                      suppress.messages = TRUE) +
  settings_optimx(method = c("L-BFGS-B")) +
  scale_conc(dose_norm = TRUE, log10_trans = FALSE) +
  stat_error_model(error_group = vars(Chemical, Species, Reference))

@@

@@

>>>>

```{r Final_Options}
my_pk <- minimal_pk +
  facet_data(vars(Chemical, Species)) +
  settings_preprocess(keep_data_original = TRUE,
                      suppress.messages = FALSE) +
  settings_optimx(method = c("L-BFGS-B")) +
  scale_conc(dose_norm = TRUE, log10_trans = FALSE) +
  stat_error_model(error_group = vars(Chemical, Species, Reference))

@@

### Figure 4A-2: Alternate version of Figure 4A

This alternate version of Figure 4A aims to simplify the assessment of replication
of datasets in invivoPKfit. In contrast to the original 4A, this will also result
in the inclusion of datasets with recorded standard deviation values
(i.e. non-indivudual animal data/summarized data).

The way this will work is by calculating the average and standard deviations
of individual animal data
(eliminating individual animal data that does not have replicates)
then testing the following:

$$
\frac{\mu + 2\sigma}{\mu} \leq 2
$$

Which essentially tests whether, at least 95% of data is within a factor of 2.
The result is a bar chart that shows how many timepoints with replicate values
passed this test. It minimizes the double (or more) counting of timepoints with
multiple replicates from individual animal data.

```{r fig4A-2-alt}
iad_summary <- cvt %>% filter(conc > 0, n_subjects_in_series == 1) %>%
  group_by(analyte_dtxsid, species, administration_route_normalized,
           conc_medium_normalized, dose_level_corrected, document_id,
           time_hr) %>%
  filter(n() > 1) %>%
  summarize(conc_sd_calc = sd(conc),
            conc_avg_calc = mean(conc),
            n_subjects_in_series = n())

sud_summary <- cvt %>% filter(conc > 0,
                              n_subjects_in_series > 1,
                              !is.na(conc_sd_normalized)) %>%
  mutate(conc_sd_calc = conc_sd_normalized,
         conc_avg_calc = conc) %>%
  distinct(analyte_dtxsid, species, administration_route_normalized,
           conc_medium_normalized, dose_level_corrected, document_id,
           time_hr, conc_sd_calc, conc_avg_calc, n_subjects_in_series)

combined_summary <- bind_rows(sud_summary, iad_summary) %>%
  rowwise() %>%
  mutate(twofold_95 = ifelse((conc_avg_calc + (2*conc_sd_calc))/conc_avg_calc < 2,
                             TRUE, FALSE))

# With the mapped column names

iad_summary <- all_my_data %>% filter(Conc > 0, N_Subjects == 1, Dose > 0) %>%
  group_by(Chemical, Species, Route, Media, Dose, Reference, Time) %>%
  filter(n() > 1) %>%
  summarize(conc_sd_calc = sd(Conc),
            conc_avg_calc = mean(Conc),
            n_subjects_in_series = n())

sud_summary <- all_my_data %>% filter(Conc > 0, N_Subjects > 1,
                                      !is.na(Conc_SD), Dose > 0) %>%
  mutate(conc_sd_calc = Conc_SD,
         conc_avg_calc = Conc,
         n_subjects_in_series = N_Subjects) %>%
  distinct(Chemical, Species, Route, Media, Dose, Reference, Time,
           conc_sd_calc, conc_avg_calc, n_subjects_in_series)

combined_summary <- bind_rows(sud_summary, iad_summary) %>%
  rowwise() %>%
  mutate(twofold_95 = ifelse((conc_avg_calc + (2*conc_sd_calc))/conc_avg_calc < 2,
                             TRUE, FALSE))

@@

### Figure 5Alt

```{r fig5Alt}
this_preds <- inner_join(predict(my_pk), winmodel) %>%
  rowwise() %>% mutate(foldPred = Conc_est/Conc) %>%
  distinct(model, method, Chemical, Species, Route, Media, Dose, Time, foldPred) %>%
  group_by(model, method, Chemical, Species, Route, Media, Dose, Time) %>%
  summarize(avgFE = mean(foldPred, na.rm = TRUE))
this_preds %>%
  inner_join(combined_summary, by = join_by(Chemical, Species,
                                            Route, Media,
                                            Dose, Time)) %>%
  filter(!is.na(model), avgFE > 0) %>% 
  # For percentages
  # ungroup() %>%
  # filter(model %in% c("model_flat")) %>%
  # count((foldPred >= 0.5 & foldPred <= 2) & !(foldConc >= 0.5 & foldConc <= 2)) %>%
  # {100*.[[2,2]]/(.[[1,2]] + .[[2,2]])}
  # For Plotting
  ggplot(aes(
    y = avgFE,
    x = twofold_95
  )) +
  geom_bin2d(bins = 40, color = NA) +
  geom_hline(yintercept = c(0.5, 2), linetype = "dashed") +
  scale_y_log10(labels = scales::label_math(format = log10),
                limits = c(0.0001, 10000)) +
  scale_fill_viridis_c(option = "cividis",
                       limits = c(1, 200),
                       oob = scales::oob_squish) +
  labs(y = "Model Error",
       x = "95% of data within 2-fold") +
  theme(aspect.ratio = 1,
        panel.border = element_rect(color = "black", fill = NA, size = 1.5),
        panel.background = element_blank(),
        panel.grid.major = element_line(color = "grey90", linewidth = 0.5),
        strip.background = element_rect(fill = "white"),
        strip.text = element_text(face = "bold"),
        axis.ticks = element_blank(),
        axis.line = element_blank())

ggsave(paste0(Sys.getenv("FIG_DIR"),
              "ModelPerformance_vDataVariability_2023-11-14.png"),
       height = 4.5,
       width = 4.5,
       device = "png",
       bg = "white",
       dpi = 300,
       units = "in")
